### 2019-08-05 frontmatter.tex
TODO and some last min corrections

%-------------------------------------------------------------------------------
% Abstract (English)
%-------------------------------------------------------------------------------
%
% COMMENT: the abstract should be limited to 2000 characters and the keywords
% to 250 characters because otherwise they will not fit in the mailing sheet.
%
% TODO: abstract in english and swedish
\begin{abstract}
    \input{abstract}
	% Access points  must work. In fact, few cryptographers would disagree with
	% the emulation of robots, which embodies the technical principles of
	% complexity theory. Hyp, our new application for lossless information, is the
	% solution to all of these challenges.
	%         %
	%         \keywords{super-lasers, space-stations, The Force, cookies.}
	%         %
\end{abstract}

@@

	\paperitem
        The code was developed by PA and Ashwin Vishnu
        Mohanan (AVM). The simulations and post-processing were performed
        by AVM. The theory was developed by PA and EL with input from AVM. A
        first version of the paper was written by PA. The final version was
        written by EL with input from AVM.
        %
	\paperitem
        The code development, the simulations and post-processing was
        handled by AVM. The paper was written by EL with input from
        AVM.
        %
    \paperitem
        The experiment was planned by the group from KTH together with the group from
        LEGI. The experimental set-up was put together by
        the group from LEGI. The experiment was carried out by the two groups
        together.
        The code for image-processing was developed by AVM, PA, Antoine
        Campagne (AC), Joel Sommeria (JS) and the code for processing
        probe data was developed by PA, RC and Diane Micard. The
        post-processing was performed by AVM, PA, AC, AS and JS.
        The paper was written by AC with input from PA, EL and AVM.
        %
    \paperitem
        The code was developed by PA, Cyrille Bonamy (CB) and AVM. The paper
        was authored by PA with input from AVM.
    \paperitem
        The code was developed by AVM, CB and PA.
        The code was benchmarked for performance by PA and AVM.
        The paper was written by AVM with inputs from PA and CB.
    \paperitem
        The code was developed by AVM, CB, Miguel Calpe Linares (MCL) and PA.
        The code was benchmarked for performance by PA and AVM.
        The paper was written by AVM with inputs from PA and CB.

@@

%TODO: fill in additional publications and conferences
%-------------------------------------------------------------------------------
% Additional publications (comment if none)
%-------------------------------------------------------------------------------
%
% \begin{otherpublications}
%         The following papers, although related, are not included in this thesis.
%
%   \paperitem%
%     {Anakin Skywalker \& Master Obi-Wan Kenobi}% Authors
%     {3639}% Year
%     {The light sabre: an elegant weapon for a more civilized age}% Title
%     {Jedi Journal of Weapons}% Journal
%     {33}% Volume
%     {2}% Number
%     {pp. 55--60}% Pages
%
% \end{otherpublications}

>>>>

%-------------------------------------------------------------------------------
% Abstract (English)
%-------------------------------------------------------------------------------
%
% COMMENT: the abstract should be limited to 2000 characters and the keywords
% to 250 characters because otherwise they will not fit in the mailing sheet.
%
\begin{abstract}
    \input{abstract}
	% Access points  must work. In fact, few cryptographers would disagree with
	% the emulation of robots, which embodies the technical principles of
	% complexity theory. Hyp, our new application for lossless information, is the
	% solution to all of these challenges.
	%         %
	%         \keywords{super-lasers, space-stations, The Force, cookies.}
	%         %
\end{abstract}

@@

	\paperitem
        The code was developed by PA and Ashwin Vishnu
        Mohanan (AVM). The simulations and post-processing were performed
        by AVM. The theory was developed by PA and EL with input from AVM. A
        first version of the paper was written by PA. The final version was
        written by EL with input from AVM.
        %
	\paperitem
        The code development, the simulations and post-processing was
        handled by AVM. The paper was written by EL with input from
        AVM.
        %
    \paperitem
        The experiment was planned by the group from KTH together with the group from
        LEGI. The experimental set-up was put together by
        the group from LEGI. The experiment was carried out by the two groups
        together.
        The code for image-processing was developed by AVM, PA, Antoine
        Campagne (AC), Joel Sommeria (JS) and the code for processing
        probe data was developed by PA, R\'emi Chassagne and Diane Micard. The
        post-processing was performed by AVM, PA, AC, AS and JS.
        The paper was written by AC with input from PA, EL and AVM.
        %
    \paperitem
        The code was developed by PA, Cyrille Bonamy (CB) and AVM. The paper
        was authored by PA with input from AVM.
    \paperitem
        The code was developed by AVM, CB and PA.
        The code was benchmarked for performance by PA and AVM.
        The paper was written by AVM with inputs from PA and CB.
    \paperitem
        The code was developed by AVM, CB, Miguel Calpe Linares and PA.
        The code was benchmarked for performance by PA and AVM.
        The paper was written by AVM with inputs from PA and CB.

@@

%TODO: fill in additional datasets
%-------------------------------------------------------------------------------
% Additional publications (comment if none)
%-------------------------------------------------------------------------------
%
% \begin{otherpublications}
%         The following papers, although related, are not included in this thesis.
%
%   \paperitem%
%     {Anakin Skywalker \& Master Obi-Wan Kenobi}% Authors
%     {3639}% Year
%     {The light sabre: an elegant weapon for a more civilized age}% Title
%     {Jedi Journal of Weapons}% Journal
%     {33}% Volume
%     {2}% Number
%     {pp. 55--60}% Pages
%
% \end{otherpublications}
